---
title: "lecture6 exercises"
output:
  pdf_document:
    latex_engine: xelatex
    extra_dependencies:
      ctexcap: UTF8
---

##### ex1
What is the population parameter?

p

What is the sample statistic?

$\hat p$

##### ex2

The law school data set law in the bootstrap package contains average LSAT and average GPA for 15 law schools. This data set is a random sample from the universe of 82 law schools in law82.

###### 1
Estimate the correlation between LSAT and GPA scores, and compute the bootstrap estimate of the standard error of the sample correlation.

```{r,include=FALSE}
library(boot)
library(bootstrap)
```

估计的相关系数为(完整的law82与sample)
```{r}
cor(law82$LSAT, law82$GPA)
(law.sample_R=cor(law$LSAT, law$GPA))
```

bootstrap得到标准差
```{r}
law.batch_num<-2000 # 迭代次数
law.sample_size<-nrow(law)
law.R_batch<-numeric(law.batch_num)

for(i in 1:law.batch_num) {
  sample_per_iter=law[sample(law.sample_size, size=law.sample_size, replace=TRUE),]
  law.R_batch[i]<-with(sample_per_iter, cor(LSAT, GPA))
}

my.law.boot_se=sd(law.R_batch)
```

```{r}
my.law.boot_se
```

###### 2
Use the boot function from package boot.


```{r}
law.boot_obj<-boot(law, function(data,index){cor(data[index,]$LSAT, data[index,]$GPA)}, R=2000)
```

```{r}
law.boot_obj$t0
sd(law.boot_obj$t)
```
对标准差得到了近似的结果(随机不可能相同).

##### ex3
###### 1
Compute the bootstrap estimation of bias for the law school sample correlation problem.

```{r}
mean(law.R_batch)-law.sample_R
```

###### 2
The patch (bootstrap) data  contains measurements of a certain hormone in the bloodstream of eight subjects after wearing a medical patch.

```{r}
patch.boot_obj<-boot(patch, function(data,index){mean(data[index,]$y)/mean(data[index,]$z)}, R=2000)
```

```{r}
patch.boot_obj
```

```{r}
mean(patch.boot_obj$t)-patch.boot_obj$t0
```
可以看到与summary给出了相同的结果

##### ex4
###### 1
Compute the confidence intervals for the patch ratio statistic.
```{r}
# norm
alpha=0.05
patch.se=sd(patch.boot_obj$t)
radius.norm=qnorm(0.025)*patch.se
print(c(patch.boot_obj$t0+radius.norm, patch.boot_obj$t0-radius.norm))
# basic
print(c(2*patch.boot_obj$t0-quantile(patch.boot_obj$t, 1-alpha/2), 2*patch.boot_obj$t0-quantile(patch.boot_obj$t, alpha/2)))
# perc
print(c(quantile(patch.boot_obj$t,alpha/2),quantile(patch.boot_obj$t,1-alpha/2)))
```
计算的是置信水平为0.05的情况.

###### 2
Compute the confidence intervals using the boot.ci function.
```{r}
(patch.boot_ci=boot.ci(patch.boot_obj,type=c("norm","basic","perc")))
```

可以看到norm与(1)相同, (2)(3)有微小的差别, 猜测是boot.ci的实现中, 对quantile做了平滑化.

##### ex5
Use linear regression model to predict cat heart weights with cat body weights. Compute the confidence intervals of the regression coefficients with bootstrap resampling.
```{r,message=FALSE}
library(MASS)
data(cats)
library(dplyr)
```

分别考虑male与female, 都是0.95的置信水平.
```{r}
female.cats=cats%>%filter(Sex=="F")
male.cats=cats%>%filter(Sex=="M")
```

```{r}
R.f<-function(data,index,k) {
  # k=1, 截距, k=2, 斜率
  fit<-lm(Hwt~Bwt, data[index,])
  return(fit$coefficients[k])
}
female.b0.ci<-boot(female.cats,statistic = R.f,R=2000,k=1)%>%boot.ci(type=c("norm","basic","perc"))
female.b1.ci<-boot(female.cats,statistic = R.f,R=2000,k=2)%>%boot.ci(type=c("norm","basic","perc"))
```

```{r}
female.b0.ci
female.b1.ci
```

我们看看lm给出的区间估计
```{r}
female.fit<-lm(Hwt~Bwt,female.cats)
```

```{r}
confint(female.fit)
```

对male进行类似的操作.
```{r}
male.b0.ci<-boot(male.cats,statistic = R.f,R=2000,k=1)%>%boot.ci(type=c("norm","basic","perc"))
male.b1.ci<-boot(male.cats,statistic = R.f,R=2000,k=2)%>%boot.ci(type=c("norm","basic","perc"))
```
```{r}
male.b0.ci
male.b1.ci
```

```{r}
male.fit<-lm(Hwt~Bwt,male.cats)
confint(male.fit)
```
看到与female的结果有很大差别, b1明显更大, 由于它的区间宽度明显小很多, 猜想应该male的样本量是要大于female, 的确如此.

```{r}
nrow(male.cats)
nrow(female.cats)
```


